### 2019-08-16 paper/spad_single/sections/introduction.tex
Realsense + starting kitti

contributions
%
\begin{itemize}
	\item We introduce the idea of augmenting an RGB camera with a single-pixel
    SPAD to address scale ambiguity error in monocular depth estimators.	
  \item We analyze our approach on indoor scenes using the NYU Depth v2 dataset.
    We demonstrate that our approach is able to resolve scale ambiguity while
    being fast and easy to implement.
	\item We build a hardware prototype and evaluate the efficacy of our
    approach on real-world data. 
\end{itemize}

>>>>

%
\subsection{Context}
Estimating depth from images is an important imaging problem, as dense depth
maps are useful precursors for high-level scene understanding tasks like
segmentation and pose estimation (cite cite cite) and mid-level perception (of
which depth estimation is an important part) has been shown to be very useful
for e.g. training robots to navigate their environments. While traditional approaches to depth
estimation use multiple cameras or structure-from-motion, convolutional neural
networks have also demonstrated reasonable performance on the so-called
monocular depth estimation task, where the network is trained to produce a dense
depth map given only a single RGB image of the scene.
\subsection{Problem Statement}
While deep monocular depth estimators have demonstrated strong performance (cite
cite) and even some generalizability across scene types, the task they are solving is fundamentally
underconstrained due to \textit{inherent scale ambiguity}, i.e. the unresolvable
tradeoff between size and distance in monocular images. This ambiguity could be
resolved by adding an additional camera and calculating a disparity map, but
this method still fails on textureless regions and areas with lots of
occlusions. Other approaches use FMCW or time-of-flight LiDAR technologies,
but these approaches are currently expensive and bulky. 
\subsection{Proposed approach}
In this paper, we show that by augmenting the RGB image with a histogram of
depth information, we can achieve substantially improved performance
(and generalizability) over state-of-the-art monocular depth
estimators. By performing an exact, weighted histogram matching on the output
depth map of the depth estimator, we can match the depth histogram of the scene
to the depth histogram of our estimate. Such a histogram can be captured
relatively inexpensively using only a single pixel single-photon avalanche diode
(SPAD) and pulsed laser illumination diffused over the field of view.
\subsection{Impact}
Our method is a lightweight postprocessing step that substantially improves
the quality of depth maps produced by monocular depth estimators. It can be
applied to any method to improve the accuracy instantly. (Our method also
helps neural-network-based methods generalize across scene types easily.)
\subsection{Limitations}
Our method is not without limitations, however. It still requires a laser and
single-pixel detector, and as such, is sensitive to ambient photons. Our method,
which is a fundamentally a variant of histogram matching, is, like histogram
matching, unable to transpose the values of pixels (i.e. if pixel $a$ is farther
than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
In other words, our method is not able to resolve ordinal depth errors
(errors where an object is wrongly placed closer or farther
relative to another object). Finally, our method is non-differentiable, and is
therefore unsuitable for end-to-end optimization of multi-part networks.

\begin{itemize}
	\item We introduce the idea of augmenting an RGB camera with a single-pixel
    SPAD to address scale ambiguity error in monocular depth estimators.	
  \item We analyze our approach on indoor scenes using the NYU Depth v2 dataset.
    We demonstrate that our approach is able to resolve scale ambiguity while
    being fast and easy to implement.
  \item (Potentially) We investigate the ability of our method to 
    help generalization of monocular depth estimators across scene types. 
    We (hopefully) demonstrate that our method allows monocular depth
    estimators to perform well even on completely different scene types.
	\item We build a hardware prototype and evaluate the efficacy of our
    approach on real-world data. 
\end{itemize}
